### 2023-03-29 resilience-safe-up.tex
Adjusting 3.1
up

\subsection{Case: $\Safe=\uparrow \Safe$ and $\Bad=\uparrow \Bad$.}

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ is upward closed, there exists a finite basis $B_{\uparrow \Safe}$ such that $\uparrow \Safe = \uparrow B_{\Safe}$. 
Moreover since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS,  $\pred^*(\Safe)=\uparrow \pred^*(\Safe)$ and $\pred^*(\Safe)$ admits a finite basis $B_{\pred^*(\Safe)}$. Since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WSTS  with effective pred-basis, we may compute a finite basis of $\pred^*(\Safe)$ with the backward coverability algorithm. 
Since $\uparrow \Bad$  is upward closed, there exists a finite basis $B_{\uparrow \Bad}$ such that $\uparrow \Bad = \uparrow B_{\Bad}$. % Moreover $ \uparrow B_{\Bad} \subseteq \uparrow B_{\pred^*(\Safe)}$ iff for every $b \in B_{\Bad}$, there is a $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$.
Since $\Bad = \uparrow \Bad \setminus \Safe$, $\Bad \subseteq \uparrow B_{\pred^*(\Safe)}$ iff for every $b \in B_{\Bad}$, there is either $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$, either $t \in B_{\Safe}$ such that $t\leq b$,
% si on est dans up Bad, il faut que ou bien on soit dans pred(Safe) ou bien on soit dans Safe
hence the resilience problem is decidable.
\end{proof}

>>>>

\subsection{Case: $\Safe=\uparrow \Safe$ and $\Bad=\uparrow \Bad \setminus \Safe$.}

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ is upward closed, there exists a finite basis $B_{ \Safe}$ such that $\uparrow \Safe = \uparrow B_{\Safe}$. 
Moreover since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS,  $\pred^*(\Safe)=\uparrow \pred^*(\Safe)$ and $\pred^*(\Safe)$ admits a finite basis $B_{\pred^*(\Safe)}$. Since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WSTS  with effective pred-basis, we may compute a finite basis of $\pred^*(\Safe)$ with the backward coverability algorithm. 
Since $\uparrow \Bad$  is upward closed, there exists a finite basis $B_{\uparrow \Bad}$ such that $\uparrow \Bad = \uparrow B_{\uparrow \Bad}$. % Moreover $ \uparrow B_{\Bad} \subseteq \uparrow B_{\pred^*(\Safe)}$ iff for every $b \in B_{\Bad}$, there is a $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$.
Since $\Bad = \uparrow \Bad \setminus \Safe$, $\Bad \subseteq \uparrow B_{\pred^*(\Safe)}$ iff for every $b \in B_{\Bad}$, there is either $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$, either $t \in B_{\Safe}$ such that $t\leq b$,
% si on est dans up Bad, il faut que ou bien on soit dans pred(Safe) ou bien on soit dans Safe
hence the resilience problem is decidable.
\end{proof}
